Psychophysics of musical elements in the discrete-time representation of sound

### 2017-07-02 article/acm/body.tex
terminada revisao inicial de todas as figuras e tabelas

\begin{figure}[h!]
    \centering
        \includegraphics[width=\columnwidth]{figures/movContraponto}
    \caption{Different motions of counterpoint aiming to preserve independence
        between voices. There are 3 types of motion: direct, contrary and
        oblique. The parallel motion is a type of direct motion.}
        \label{fig:movContraponto}
\end{figure}

@@

\begin{table*}[htp!]
\tiny
\centering
\caption{Transition of durations heard individually until it turns into pitch.}
\begin{tabular}{  l | r r r r   r r r    r r r || r r || r r r r r r }
\hline
           & \multicolumn{10}{c}{$\underleftarrow{\text{\bf perception zone of
           duration as rhythm}}$} & \multicolumn{2}{c}{transition} & \multicolumn{3}{c}{-} \\
duration (s) & {\bf ...}     & {\bf 32,}     & {\bf 16,}   & {\bf 8,}  & {\bf 4,}   & {\bf 2,}   & {\bf 1,}   & {\bf 1/2,} & {\bf 1/4,} & {\bf 1/8,} & $\frac{1}{16}=62,5ms$ , & $\frac{1}{20}=50ms$ & {\color{gray} 1/40} & {\color{gray} 1/80  } & {\color{gray} 1/160 } & {\color{gray} 1/320 } & {\color{gray} 1/640 } & {\color{gray} ... } \\
frequency (Hz) & {\color{gray} ...} & {\color{gray} 1/32,}   & {\color{gray} 1/16,} & {\color{gray} 1/8,} & {\color{gray} 1/4,} & {\color{gray} 1/2,} &  {\color{gray} 1,}  & {\color{gray} 2,}   & {\color{gray} 4,}   & {\color{gray} 8,}    & 16,  & 20   & {\bf 40}   & {\bf 80}   & {\bf 160}   & {\bf 320}   & {\bf 640}   & {\bf ...} \\
           & \multicolumn{10}{c}{ - } & \multicolumn{2}{c}{transition}
           & \multicolumn{6}{c}{$\overrightarrow{\text{\bf perception zone of
           duration as pitch}}$} \\
\hline
\end{tabular}
\label{tab:duracoes}
\end{table*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.9\textwidth]{figures/metricaMusical_}
    \caption{Divisions and groupings of the musical pulse for establishing a metric. Divisions of the quarter note, regarded as the
        pulse, is presented on the left. The time signature yielded by
        groupings of the music pulse is presented on the right.}
        \label{fig:pulsoSubAgl}
\end{figure*}

@@

\begin{figure}
    \centering
        \includegraphics[width=\columnwidth]{figures/climax}
        \caption{Canonical distinctions of musical climax in a given melody and
        other domains. The possibilities considered are: climax at the beginning, at the first half, in the middle, in the second half and 
        at the end. The x and y-axis is not properly specified since the parameters can be non-existent, as in a reference structure.}
        \label{fig:climax}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
        \includegraphics[width=.8\columnwidth]{figures/movContraponto_}
    \caption{Different motions of counterpoint aiming to preserve independence
        between voices. There are 3 types of motion: direct, contrary and
        oblique. The parallel motion is a type of direct motion.
	A voice is often called a 'melodic line' or a melody.}
        \label{fig:movContraponto}
\end{figure}

@@

\begin{table*}[htp!]
\caption{Transition of durations heard as rhythm until heard as pitch.}
\begin{tabular}{  l | r r r r   r r r    r r r || r r  } \hline
& \multicolumn{10}{c}{\bf perception of durations as rhythm} & \multicolumn{2}{c}{}  \\
	duration (s) & \multirow{2}{*}{\bf ...}     & {\bf 32,}     & {\bf 16,}   & {\bf 8,}  & {\bf 4,}   & {\bf 2,}   & {\bf 1,}   & {\bf 1/2,} & {\bf 1/4,} & {\bf 1/8,} & \multirow{2}{*}{ ... transition } & \\
frequency (Hz) & & {\color{gray} 1/32,}   & {\color{gray} 1/16,} & {\color{gray} 1/8,} & {\color{gray} 1/4,} & {\color{gray} 1/2,} &  {\color{gray} 1,}  & {\color{gray} 2,}   & {\color{gray} 4,}   & {\color{gray} 8,} & & \\
& \multicolumn{10}{c}{ - } & \multicolumn{2}{c}{} \\ \hline
\end{tabular}
\vspace{.2cm}

	\begin{tabular}{  l | p{1.7cm}  || r r || r } \hline
& \multicolumn{1}{c}{} & \multicolumn{2}{c}{transition} &  \\
duration (s) & \multirow{2}{*}{\bf rhythm ...} & $\frac{1}{16}=62.5ms$ , & $\frac{1}{20}=50ms$ & \multirow{2}{*}{\bf ... pitch} \\
frequency (Hz) & & 16, & 20 &  \\
& \multicolumn{1}{c}{} & \multicolumn{2}{c}{transition} & \\ \hline
\end{tabular}
\hspace{3.36cm}
\vspace{.2cm}

	\begin{tabular}{  l | p{1.7cm} || r r r r r r }\hline
& \multicolumn{1}{c}{} &  \\
	duration (s) & \multirow{2}{*}{transition ...} & {\color{gray} 1/40} & {\color{gray} 1/80  } & {\color{gray} 1/160 } & {\color{gray} 1/320 } & {\color{gray} 1/640 } & \multirow{2}{*}{\bf ... } \\
frequency (Hz) & & {\bf 40}   & {\bf 80}   & {\bf 160}   & {\bf 320}   & {\bf 640}   & \\
& \multicolumn{1}{c}{} & \multicolumn{6}{c}{\bf perception of durations as pitch} \\ \hline
\end{tabular}
\hspace{2.70cm}
\label{tab:duracoes}
\end{table*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=.9\textwidth]{figures/metricaMusical__}
    \caption{Divisions and groupings of the musical pulse for establishing a metric. Divisions of the quarter note, regarded as the
        pulse, is presented on the left. The time signature yielded by
        groupings of the music pulse is presented on the right.}
        \label{fig:pulsoSubAgl}
\end{figure*}

@@

\begin{figure}
    \centering
        \includegraphics[width=.8\columnwidth]{figures/climax_}
        \caption{Canonical distinctions of musical climax in a given melody and
        other domains. The possibilities considered are: climax at the beginning, at the first half, in the middle, in the second half and 
        at the end. The x and y-axis is not properly specified since the parameters can be non-existent, as in a reference structure.}
        \label{fig:climax}
\end{figure}
